### 2014-04-24 article.tex
Add in text for effects of CC, work on layout, show where boreholes are in map.

% TODO: Location map of Karup in Denmark + locations of boreholes/rivers.

@@

% TODO: Mike she schematic figure (maybe from thompson2004application).

@@

@@

\subsection{Climate change scenario}

To simulate climate change in 2050, three different emissions scenarios were used. These were Low, Medium and High, and for each one of these new preipitation and evapotsranspiration time series were produced (one for each station in the case of precipitation). The model was then re-run with these new input data.

Below are some figures which demonstrate the fit between the modelled and observed values.

\begin{figure}[!h]
    \centering
    \includegraphics[width=15cm]{geogg101_screenshots/practical2/borehole_cal}
    \caption{Simulated (blue line) plotted against observed (black crosses) for the four boreholes.}
    \label{fig:borehole_cal}
\end{figure}

\begin{figure}[!h]
    \centering
    \includegraphics[width=15cm]{geogg101_screenshots/practical2/river_cal}
    \caption{Simulated (blue line) plotted against observed (black crosses) for the discharge stations.}
    \label{fig:river_cal}
\end{figure}

\begin{figure}[!h]
    \centering
    \includegraphics[width=15cm]{geogg101_screenshots/practical2/borehole_scatter}
    \caption{Scatter graphs of observed (horizontal axis) vs simulated (vertical axis) for each of the four boreholes and the calibration/validation periods. The blue line shows the line of best fit and the corresponding R value is shown. All values are in \SI{}{metres}.}
    \label{fig:borehole_scatter}
\end{figure}

\begin{figure}[!h]
    \centering
    \includegraphics[width=15cm]{geogg101_screenshots/practical2/river_scatter}
    \caption{Scatter graphs of observed (horizontal axis) vs simulated (vertical axis) for both rivers and the calibration/validation periods. The blue line shows the line of best fit and the corresponding R value is shown. All values are in \SI{}{cumecs}.}
    \label{fig:river_scatter}
\end{figure}

\begin{figure}[!h]
    \centering
    \includegraphics[width=15cm]{geogg101_screenshots/practical2/ctrl_river_regime}
    \caption{Simulated and observed river regimes calculated over the combined calibration and validation periods.}
    \label{fig:ctrl_river_regime}
\end{figure}

\newpage
\subsection{Effects of climate change}

>>>>

\begin{figure}[!h]
    \centering
    \includegraphics[height=8cm]{geogg101_screenshots/practical2/karup_catchment_with_boreholes}
    \caption{Location of Karup Catchment in Denmark, with the main rivers and the four boreholes used for observation shown. Adapted from \textcite{blasone2008uncertainty}.}
    \label{fig:karup_catchment}
\end{figure}

@@

@@

According to the guidelines provided by \textcite{henriksen2008assessment}, an NSE greater than $0.85$ should be considered as having an `excellent' fit with the observed data. For the validation period and the two discharge stations in Table \ref{table:summary_stats}, their values for NSE are $0.97$ and $0.92$, so the fit with the observed data is `excellent'

@@

As can be seen in Figure \ref{fig:ctrl_river_regime}, the river simulated river regime also matches the observed regime quite closely. The largest discrepency is during August for the Hagebro discharge station, when the simulated results overestimate the monthly discharge by 8\%. In general, the model tends to overestimate the discharge in the summer months when the discharge is at its lowest. Likewise, it underestimates the discharge in the winter months when the discharge is at its highest.

\begin{figure}[!h]
    \centering
    \includegraphics[height=9cm]{geogg101_screenshots/practical2/ctrl_river_regime}
    \caption{Simulated and observed river regimes calculated over the combined calibration and validation periods.}
    \label{fig:ctrl_river_regime}
\end{figure}

\newpage

When looking at the individual graphs for the four boreholes and two discharge stations (Figures \ref{fig:borehole_cal} and \ref{fig:river_cal}), the model appears to match the observations well, both for the calibration and the validation period. (In Figure \ref{fig:river_cal} the simulated line is obscured by the observed.)

\begin{figure}[!h]
    \centering
    \includegraphics[width=14.5cm]{geogg101_screenshots/practical2/borehole_cal}
    \caption{Simulated (blue line) plotted against observed (black crosses) for the four boreholes.}
    \label{fig:borehole_cal}
\end{figure}

\begin{figure}[!h]
    \centering
    \includegraphics[width=14.5cm]{geogg101_screenshots/practical2/river_cal}
    \caption{Simulated (blue line) plotted against observed (black crosses) for the discharge stations.}
    \label{fig:river_cal}
\end{figure}

\newpage
Scatter graphs of the boreholes and discharge station again show that the model performs reasonably well at reproducing the observed data, with relatively few outliers visible. It backs up the findings from Figure \ref{fig:ctrl_river_regime} that the model overestimates the periods of low flow (summer) and underestimates those of high (winter), which can be seen by the gradient of the lines of best fit which are less than one.

\begin{figure}[!h]
    \centering
    \includegraphics[width=12cm]{geogg101_screenshots/practical2/borehole_scatter}
    \caption{Scatter graphs of observed (horizontal axis) vs simulated (vertical axis) for each of the four boreholes and the calibration/validation periods. The blue line shows the line of best fit and the corresponding R value is shown. All values are in \SI{}{metres}.}
    \label{fig:borehole_scatter}
\end{figure}

\begin{figure}[!h]
    \centering
    \includegraphics[width=12cm]{geogg101_screenshots/practical2/river_scatter}
    \caption{Scatter graphs of observed (horizontal axis) vs simulated (vertical axis) for both rivers and the calibration/validation periods. The blue line shows the line of best fit and the corresponding R value is shown. All values are in \SI{}{cumecs}.}
    \label{fig:river_scatter}
\end{figure}

\newpage

\subsection{Effects of climate change}

To simulate climate change in 2050, three different emissions scenarios were used. These were Low, Medium and High, and for each one of these new preipitation and evapotsranspiration time series were produced (one for each station in the case of precipitation). The calibrated model was then re-run with these new input data. Under these three different emissions scenarios, the river regime deviated from its original regime, as can be seen in Figure \ref{fig:effects_of_cc}. Each of the regimes is plotted against the simulated calibration/validation regime (CVR), not the observed data. The Medium and High scenarios both show significant deviation from the CVR, with the effect being largest in the winter when the discharge is greatest. The Low scenario does show deviation from the CVR, although not nearly as markedly.
